Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw
Title
first sentence

\dropcap{M}ultiple comparisons are a persistent problem when developing statistical methods for scientific problems \citep{benjaminiControllingFalseDiscovery1995}. In forensic statistics, researchers have been focusing on the necessity of building up research databases which can be used to develop objective algorithms for evidence comparisons and explore closest non-matches \citep{pcast}. While these databases (and open data) are critically important in forensics, we also need to be careful about how our methods are affected by the multiple comparison problem.

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that a single conclusion is often based on  many comparisons, either implicitly or explicitly. \hh{Algorithms, in particular, make a large number of comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report\citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly to slide one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and keep track of the similarity measure.}

Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. When we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.

>>>>

\dropcap{I}n forensic evidence a single conclusion is often based on  many comparisons, either implicitly or explicitly.
Multiple comparisons are a persistent problem when developing statistical methods for scientific problems \citep{benjaminiControllingFalseDiscovery1995}.
In forensic statistics, researchers have been focusing on building up research databases to develop algorithms for objective evidence comparisons.
\hh{In practice, these algorithms then allow searches across (vast) databases and report the best $N$ matches to a particular piece of evidence, raising the critically important problem of close non-matches }\citep{pcast}.

%and explore closest non-matches . While these databases (and open data) are critically important in forensics, we also need to be careful about how our methods are affected by the multiple comparison problem.

This issue has been raised in the past with regard to DNA \citep{thompson2003} and fingerprints \citep{@fine2006}: one of the issues leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid bombing case was that the large size of the IAFIS database used to locate similar prints made it possible to locate `unusually' similar non-matches.

 \hh{Algorithms, in particular, make a large number of implicit comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report \citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly} \svp{sliding} \hh{one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and} \svp{keeping} \hh{track of the similarity measure.}
\svp{This mirrors the forensic examination process, as examiners visually}
rotate or align two pieces of evidence under comparison microscopes.

%An explicit search, in constrast, occurs when we conduct database searches.
%These searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.
